---
title:
author:
output:
  officedown::rdocx_document:
    reference_docx: report_template.docx
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = "allow")
```

```{r source, warning = FALSE, include = FALSE}
source("Code/helper.scripts/Bootstrap_method_helpers_KK.R", local = knitr::knit_global())
source("Code/config.R", local = knitr::knit_global())
'%!in%' <- function(x,y)!('%in%'(x,y))
```

```{r packages, warning = FALSE, include = FALSE}
lib_list <- c("readxl","foreach","gridExtra","ggpubr","rayshader","viridis","raster",
              "gstat","rgdal","sp","spatialEco","HTSSIP","hablar",
              "data.table","tidyverse","boot","GPArotation","psych","cowplot",
              "pander", "flextable", "officer", "officedown")


Load_Libs(lib_list)
```

```{r speclist, warning = FALSE, include = FALSE}
SPP <- tolower(c("Arctic skua", "Arctic tern", "common gull", "common tern", "fulmar", "gannet", "great black-backed gull", "great skua", "herring gull", "kittiwake", "lesser black-backed gull", "little gull", "Manx shearwater", "pomarine skua", "red-throated diver", "sandwich tern", "sooty shearwater"))
```

```{r import data, warning = FALSE, include = FALSE}
# bootstrapped flight heights
reflist <- list.files("Code/outputs/SppDat", full.names = TRUE)

SppDat <- data.table::rbindlist(lapply(reflist,function(x) readxl::read_xlsx(x,sheet="Sheet1")),
                      use.names=TRUE,fill=TRUE)

SppDat <- SppDat[order(SppDat$`Survey Date`),]

SppDat$month <- factor(SppDat$month, levels = c("March", "April", "May", "June", "July", "August", "September", "October", "November", "December", "January", "February"))

# This creates column to split between years 1 and 2 if needed. 
SppDat$yr <- "Year 1"

SppDat$yr[as.Date(SppDat$`Survey Date`) %!in% Date1:Date2] <- "Year 2"
```

```{r import measure data, warning = FALSE, include = FALSE}
# all data
measurelist <- list.files("Code/outputs/MeasureDat", full.names = TRUE)

MeasureDat <- rbindlist(lapply(measurelist, function(x) readxl::read_xlsx(x,sheet = "Sheet1")),
                        use.names = TRUE, fill = TRUE)

MeasureDat <- MeasureDat[order(MeasureDat$`Survey Date`),]

# This creates column to split between years 1 and 2 if needed. 
MeasureDat$yr <- "Year 1"

MeasureDat$yr[as.Date(MeasureDat$`Survey Date`) %!in% Date1:Date2] <- "Year 2"

load(file = "Code/outputs/reflectcount")
```

```{r shapefile, warning = FALSE, include = FALSE}
# shapearea <- raster::shapefile(boundary.shapefile)
# shapearea <- spTransform(shapearea,WGS84)
# shapefileDF <- fortify(shapearea)
# e <- extent(shapearea)
# # coerce to a SpatialPolygons object
# p <- as(e, 'SpatialPolygons')  
# proj4string(p) <- sf::st_crs(4326)$proj4string

shapearea2 <- raster::shapefile(boundary.2)
shapearea2 <- spTransform(shapearea2,WGS84)
shapefile2DF <- fortify(shapearea2)
e2 <- extent(shapearea2)
# coerce to a SpatialPolygons object
p2 <- as(e2, 'SpatialPolygons')  
proj4string(p2) <- sf::st_crs(4326)$proj4string

shapearea3 <- raster::shapefile(boundary.3)
shapearea3 <- spTransform(shapearea3,WGS84)
shapefile3DF <- fortify(shapearea3)
e3 <- extent(shapearea3)
# coerce to a SpatialPolygons object
p3 <- as(e3, 'SpatialPolygons')  
proj4string(p3) <- sf::st_crs(4326)$proj4string
```

```{r wide to long format, warning = FALSE, include = FALSE}
all.frame <- SppDat %>% dplyr::select(Species,lwheight,mdheight,hiheight,month, year, yr, loc)

## Gathers the frame into LONG format for plotting
all.frame <- gather(all.frame,category,out,lwheight:hiheight)
all.frame$category <- plyr::revalue(all.frame$category,c("lwheight"="Low",
                                                         "mdheight"="Mean",
                                                         'hiheight'="High"))

all.frame$category <- factor(all.frame$category, levels=c("Low","Mean","High"))

all.frame$yr <- factor(all.frame$yr, levels = c("Year 1", "Year 2"))

all.frame$month <- factor(all.frame$month, levels = c("March", "April", "May", "June", "July", "August", "September", "October", "November", "December", "January", "February"))
```

```{r for loops, warning = FALSE, include = FALSE}
yrs <- c("Year 1", "Year 2")
locs <- c("SG2", "SG3")
```

\allsectionsfont{\centering}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

<!-- This will make up the first page -->
<!-- The vspace function will say how much space to leave from the previous entry -->
<!-- In this case vspace of 3cm means 3cm from the top of the page.  -->

Digital video aerial surveys of seabirds at Seagreen 2 & 3:

March 2019 to February 2021

Flight height analysis

\nextpage

# Results

## Flight Height

  Estimates of mean flight height for the minimum, mean and maximum flight height scenarios are presented for each species in Tables `r run_reference("pch_kittiwake")` - `r run_reference("pch_lesser_black-backed_gull")`. The estimate of the proportion of birds at PCH for each scenario is based on the number of individual birds whose mean flight height fell within the rotor swept area.

  The distribution of these heights are presented as box plots for each species in Figures `r run_reference("mainboxplot_kittiwake")`, `r run_reference("mainboxplot_gannet")` and `r run_reference("mainboxplot_lesser_black-backed_gull")`. The grey boxes represent the middle 50% of the estimated flight heights for each scenario, and the mean of the population is indicated by the black dot. The distributions of flight height are also represented in ordered dot plots in Figures `r run_reference("Datplot_kittiwake")`, `r run_reference("Datplot_gannet")` and `r run_reference("Datplot_lesser_black-backed_gull")`.

  The spatial variation in flight heights are represented in Figures X.

  All but one of the mean heights for either of the two species ranged below `r turbine.high`m (the maximum rotor height of the smallest turbine specification). As such, the estimated proportions of birds at PCH for the smallest and largest wind turbine scenarios are identical with the exception of the maximum July flight height for gannets.

<!---BLOCK_LANDSCAPE_START--->
### Kittiwake
```{r k, include = FALSE}
i <- "kittiwake"
```
#### Proportion of birds at PCH
```{r kitti pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges
 
  For interpretation of the following graphs, see Section 3.2. 


```{r kitti_boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r kitti blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height

```{r k12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r kitti spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r k22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r kitti spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r k13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r kitti spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r k23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r kitti spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->



<!---BLOCK_LANDSCAPE_START--->
### Gannet
```{r g, include = FALSE}
i <- "gannet"
```
#### Proportion of birds at PCH
```{r gannet pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r gannet boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r gannet blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height

```{r g12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r gannet spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r g22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r gannet spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r g13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r gannet spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r g23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r gannet spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

<!---BLOCK_LANDSCAPE_STOP--->


<!---BLOCK_LANDSCAPE_START--->
### Lesser black-backed gull
```{r l, include = FALSE}
i <- "lesser black-backed gull"
```
#### Proportion of birds at PCH
```{r lbbg pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```


#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r lbbg boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r lbbg blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height

```{r lbbg12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r lbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r lbbg22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r lbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r lbbg13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r lbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r lbbg23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r lbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->

<!---BLOCK_LANDSCAPE_START--->

### Great black-backed gull
```{r gb, include = FALSE}
i <- "great black-backed gull"
```
#### Proportion of birds at PCH
```{r gbbg pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r gbbg boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r gbbg blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height

```{r gbbg12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r gbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r gbbg22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r gbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r gbbg13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r gbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r gbbg23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r gbbg spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->

<!---BLOCK_LANDSCAPE_START--->

### Herring gull

```{r h, include = FALSE}
i <- "herring gull"
```
#### Proportion of birds at PCH
```{r herring pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r herring boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r herring blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r herring12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r herring spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r herring22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r herring spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r herring13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r herring spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r herring23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r herring spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->

<!---BLOCK_LANDSCAPE_START--->

### Fulmar

```{r f, include = FALSE}
i <- "fulmar"
```
#### Proportion of birds at PCH
```{r fulmar pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r fulmar boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r fulmar blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r fulmar12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r fulmar spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r fulmar22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r fulmar spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r fulmar13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r fulmar spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r fulmar23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r fulmar spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->

<!---BLOCK_LANDSCAPE_START--->

### Common gull

```{r cg, include = FALSE}
i <- "common gull"
```
#### Proportion of birds at PCH
```{r common gull pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r common gull boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r common gull blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r commongull12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r common gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commongull22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r common gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commongull13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r common gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commongull23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r common gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->


<!---BLOCK_LANDSCAPE_START--->

### Arctic tern

```{r at, include = FALSE}
i <- "arctic tern"
```
#### Proportion of birds at PCH
```{r arctic tern pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r arctic tern boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r arctic tern blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r arctictern12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r arctic tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r arctictern22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r arctic tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r arctictern13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r arctic tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r arctictern23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r arctic tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->



<!---BLOCK_LANDSCAPE_START--->

### Great skua

```{r gs, include = FALSE}
i <- "great skua"
```
#### Proportion of birds at PCH
```{r great skua pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r great skua boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r great skua blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r greatskua12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r great skua spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r greatskua22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r great skua spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r greatskua13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r great skua spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r greatskua23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r great skua spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->


<!---BLOCK_LANDSCAPE_START--->

### Sandwich tern

```{r st, include = FALSE}
i <- "sandwich tern"
```
#### Proportion of birds at PCH
```{r sandwich tern pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r sandwich tern boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r sandwich tern blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r sandwichtern12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r sandwich tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r sandwichtern22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r sandwich tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r sandwichtern13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r sandwich tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r sandwichtern23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r sandwich tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->


<!---BLOCK_LANDSCAPE_START--->

### Common tern

```{r ct, include = FALSE}
i <- "common tern"
```
#### Proportion of birds at PCH
```{r common tern pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r common tern boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r common tern blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r commontern12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r common tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commontern22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r common tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commontern13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r common tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r commontern23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r common tern spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->



<!---BLOCK_LANDSCAPE_START--->

### Little gull

```{r lg, include = FALSE}
i <- "little gull"
```
#### Proportion of birds at PCH
```{r little gull pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r little gull boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r little gull blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r littlegull12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r little gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r littlegull22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r little gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r littlegull13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r little gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r littlegull23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r little gull spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->



<!---BLOCK_LANDSCAPE_START--->

### Manx shearwater

```{r ms, include = FALSE}
i <- "manx shearwater"
```
#### Proportion of birds at PCH
```{r manx shearwater pch table print, child = "Tables_Figures/Table_PCH.Rmd", warning = FALSE}
```
#### Flight height ranges

  For interpretation of the following graphs, see Section 3.2. 

```{r manx shearwater boxplot, child = "Tables_Figures/Boxplots.Rmd", warning = FALSE}
```

```{r manx shearwater blueplot, child = "Tables_Figures/Blue_plot.Rmd", warning = FALSE}
```
#### Spatial variation in flight height
```{r manxshearwater12, include = FALSE}
j <- 1
k <- 1
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r manx shearwater spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r manxshearwater22, include = FALSE}
j <- 1
k <- 2
shapefileDF <- shapefile2DF
p <- p2
shapearea <- shapearea2
```

```{r manx shearwater spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r manxshearwater13, include = FALSE}
j <- 2
k <- 1
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r manx shearwater spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```

```{r manxshearwater23, include = FALSE}
j <- 2
k <- 2
shapefileDF <- shapefile3DF
p <- p3
shapearea <- shapearea3
```

```{r manx shearwater spatial, child = "Tables_Figures/Spatial_plots.Rmd", warning = FALSE, echo = FALSE, message = FALSE}
```
<!---BLOCK_LANDSCAPE_STOP--->